Resurgence of the Airy function \\ and other exponential integrals

### 2023-02-26 exp-resurgence.tex
updates

@@

The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
\begin{align*}
& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
\end{align*}
as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}. Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
\color{DarkCyan}
Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
where $\zeta = -1 + \zeta_{-1}$.
\color{black}
\subsubsection{Lifting to a countable cover}
Formula~\ref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$. Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.

Setting $u = \cosh(t/n)$ and recalling that
\begin{align*}
\cosh(n\tau) & := T_n(\cosh(\tau)) \\
\sinh(m\tau) & := U_{m-1}(\cosh(\tau)) \sinh(\tau),
\end{align*}
we can rewrite formula~\ref{integral:mod-bessel-rational} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
\begin{align}
\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
\end{align}
For any $\nu \in \C \smallsetminus \Z$, formulas~10.27.4 and 10.32.12 from \cite{dlmf} tell us that
\begin{align}
\notag K_\nu(z) & = \frac{\pi}{\sin(\nu \pi)} \cdot \frac{1}{2}\big[ I_{-\nu}(z) - I_\nu(z) \big] \\
\notag & = \frac{1}{2i \sin(\nu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\nu t} - e^{-\nu t}\right]\,dt \\
\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\nu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\nu t)\,dt,
\end{align}
where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$. The integral converges when $z$ is in the right half-plane. We get formula~\ref{integral:mod-bessel-lifted} when we choose a rational parameter $\nu = m/n$.

When $\nu$ goes to $0$, formula~\ref{integral:mod-bessel-lifted} becomes
\[ K_\nu(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
\begin{align*}
K_\nu(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
\end{align*}
with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
\subsubsection{Link to dihedral triangulations}
Here are the local normal forms of Kummer's first and second solutions. In the table, $[\bullet]$ denotes a local holomorphic function of order $0$ \cite[identities 15.8.2--4]{dlmf}, and
\begin{align*}
a' & = a+(1-c) \\
b' & = b+(1-c) \\
c' & = 2-c
\end{align*}
\begin{center}
\begin{tabular}{c|c|c|c}
Function & $0$ & $1$ & $\infty$ \\ \hline
$F(a, b, c, \xi)$ & $[\bullet]$ & $[\bullet] + (1-\xi)^{c-a-b} [\bullet]$ & $(1/\xi)^a [\bullet] + (1/\xi)^b [\bullet]$ \\
$\xi^{1-c} F(a', b', c', \xi)$ & $\xi^{1-c} [\bullet]$ & $[\bullet] + (1-\xi)^{c-a-b} [\bullet]$ & $(1/\xi)^a [\bullet] + (1/\xi)^b [\bullet]$
\end{tabular}
\end{center}

For example, at $\zeta = \infty$, the function
\[ u_{-1} = F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, 1 - \tfrac{1}{2} \zeta_{-1}) \]
is slight, with normal form $(1/\zeta_{-1})^{1 - m/n} f_1 + (1/\zeta_{-1})^{1 + m/n} f_2$~\cite[identity~15.8.3]{dlmf}. At $\zeta = 1$, it's holomorphic with order $0$. At $\zeta = -1$, it has the form $h + \zeta_{-1}^{-1/2} f$, where $h$ is holomorphic with order $0$.

On the other hand, the function
\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}) \]
is slight at $\zeta = \pm 1$ with order $-\tfrac{1}{2}$, and slight at $\infty$ with order $1 - \tfrac{m}{n}$.

Hence, the ratio $u_{-1} / v_{-1}$ looks like a holomorphic multiple of $\zeta_1^{1/2}$ near $\zeta = 1$, a holomorphic function plus a holomorphic multiple of $\zeta_{-1}^{1/2}$ near $\zeta = -1$, and a holomorphic function plus a holomorphic multiple of $(1/\zeta_{-1})^{2m/n}$ near $\zeta = \infty$. This is consistent with $u_{-1}/v_{-1}$ being a conformal map that sends the upper half-plane to a triangle with interior angle $\pi/2$ at the images of $\zeta = \pm 1$ and interior angle $2\pi\,\tfrac{m}{n}$ at the image of $\infty$.

\color{ForestGreen}
Let's try to get the small tetrahedral tiling by setting
1 - c & = \tfrac{1}{3} \\
c - a - b & = \tfrac{1}{3} \\
b - a & = \tfrac{1}{2},
so $(a, b, c) = (-\tfrac{1}{12}, \tfrac{5}{12}, \tfrac{2}{3})$. The general hypergeometric equation is
\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + \big[c - (a+b+1)\xi_1\big] \tfrac{\partial}{\partial \xi_1} - ab\right] & v = 0 \\
\left[-\tfrac{1}{2}\zeta_1 (1 + \tfrac{1}{2}\zeta_1) 4 \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + \big[c + \tfrac{1}{2}(a+b+1)\zeta_1\big] (-2) \tfrac{\partial}{\partial \zeta_1} - ab\right] & v = 0 \\
\left[-\zeta_1 (2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 - \big[2c + (a+b+1)\zeta_1\big] \tfrac{\partial}{\partial \zeta_1} - ab\right] & v = 0 \\
\left[(1 - \zeta)(1 + \zeta) \big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[2c + (a+b+1)(\zeta - 1)\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
\left[(1 - \zeta^2)\big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[(c - a - b) + (c - 1) + (a+b+1)\zeta\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
\left[(1 - \zeta^2)\big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[\mu - \lambda + (a+b+1)\zeta\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
\left[\big[\tfrac{\partial}{\partial \zeta} \circ (1 - \zeta^2) + 2\zeta\big] \tfrac{\partial}{\partial \zeta} - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1)\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - ab\right] & v = 0 \\
\left[\tfrac{\partial}{\partial \zeta} \circ \big[ \tfrac{\partial}{\partial \zeta} \circ (1 - \zeta^2) + 2\zeta \big] + 2\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1)\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - ab\right] & v = 0 \\
\left[\big[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) + 4 \tfrac{\partial}{\partial \zeta} \circ \zeta - 2 \big] - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1) \tfrac{\partial}{\partial \zeta} \circ \zeta + \big[ (a+b+1) - ab \big]\right] & v = 0 \\
\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (3-a-b) \tfrac{\partial}{\partial \zeta} \circ \zeta + \big[ {-}1 + a + b - ab \big]\right] & v = 0 \\
\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (3-a-b) \tfrac{\partial}{\partial \zeta} \circ \zeta - (a-1)(b-1)\right] & v = 0 \\
\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta^2 - 1) + (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (a+b-3) \tfrac{\partial}{\partial \zeta} \circ \zeta + (a-1)(b-1)\right] & v = 0,
For the tetrahedral tiling, we get
\[ \left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big(\zeta^2 - 1\big) - \tfrac{8}{3} \tfrac{\partial}{\partial \zeta} \circ \zeta + \tfrac{7 \cdot 13}{12^2}\right] v = 0, \]
which comes from the integral equation
\[ \left[\big(\zeta^2 - 1\big) - \tfrac{8}{3}\,\fracderiv{-1}{\zeta}{\alpha} \circ \zeta + \tfrac{7 \cdot 13}{12^2}\,\fracderiv{-2}{\zeta}{\alpha}\right] v = 0. \]
In the frequency domain, this equation becomes
\[ \left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + \tfrac{8}{3}\,z^{-1} \tfrac{\partial}{\partial z} + \tfrac{7 \cdot 13}{12^2}\,z^{-2}\right] \laplace_{\zeta, \alpha} v = 0. \]
\color{SpringGreen}
Set
\[ \laplace_{\zeta, \alpha} v = \int_\Lambda e^{-zf}\,p\,du. \]
Observe that
\[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] \int_\Lambda e^{-zf}\,p\,du = \int_\Lambda e^{-zf}\,(f^2 - 1)p\,du \]
and
z^{-1} \tfrac{\partial}{\partial z} \int_\Lambda e^{-zf}\,p\,du & = z^{-1} \int_\Lambda e^{-zf}\,(-fp)\,du \\
& = -z^{-1} \int_\Lambda e^{-zf}\,(-zf')q_1\,du \\
& = \int_\Lambda e^{-zf}\,f'q_1\,du
where $q_1' = -fp$.
and
z^{-2} \int_\Lambda e^{-zf}\,p\,du
& = -z^{-2} \int_\Lambda e^{-zf}\,(-zf')p_1\,du \\
& = z^{-1} \int_\Lambda e^{-zf}\,f'p_1\,du \\
& = -z^{-1} \int_\Lambda e^{-zf}\,(-zf')p_2\,du \\
& = \int_\Lambda e^{-zf}\,f'p_2\,du \\
with $p_1' = p$ and $p_2' = f'p_1$.
\[ \left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + \tfrac{8}{3}\,z^{-1} \tfrac{\partial}{\partial z} + \tfrac{7 \cdot 13}{12^2}\,z^{-2}\right] \laplace_{\zeta, \alpha} v = 0. \]

\color{orange}
In DLMF notation, let's try
\begin{align*}
u_1 & = F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \xi_{-1}) \\
& = w_1(\xi_{-1}) \\
u_{-1} & = w_3(\xi_{-1}) \\
v_{-1} & = w_2(\xi_{-1}) \\
v_1 & = -i\sqrt{2}\,\zeta_1^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, -\tfrac{1}{2}\zeta_1) \\
& = (-\tfrac{1}{2}\zeta_1)^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, -\tfrac{1}{2}\zeta_1) \\
& = (1 - \tfrac{1}{2}\zeta_{-1})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, 1 - \tfrac{1}{2}\zeta_{-1}) \\
& = (1 - \xi_{-1})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, 1 - \xi_{-1}) \\
& = w_4(\xi_{-1}),
\end{align*}
where $\xi_{-1} = \tfrac{1}{2}\zeta_{-1}$.

\color{RoyalBlue}
Let's guess that we're working with the map $\phi / \psi$ with
\begin{align*}
\phi & = \frac{\Gamma(-\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{1}{2} - \tfrac{m}{2n})\Gamma(\tfrac{1}{2} + \tfrac{m}{2n})}\,(\mp \zeta)\,F(1 - \tfrac{m}{2n}, 1 + \tfrac{m}{2n}, \tfrac{3}{2}; \zeta^2) \\
& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta) - \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, -\tfrac{1}{2}\zeta_1) - \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2}\zeta_{-1}) \quad\text{[choosing negative sign]} \\
\psi & = \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(1 - \tfrac{m}{2n})\Gamma(1 + \tfrac{m}{2n})} F(\tfrac{1}{2} - \tfrac{m}{2n}, \tfrac{1}{2} + \tfrac{m}{2n}, \tfrac{1}{2}; \zeta^2) \\
& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta) + \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, -\tfrac{1}{2}\zeta_1) + \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2}\zeta_{-1}) \quad\text{[choosing negative sign]} \\
\end{align*}
\color{black}
\subsubsection{Comparison with Ghate and Venkataramana}
\begin{align*}
\mu_\text{GV} & = 1 - \left\{\frac{k_1}{d}\right\} - \left\{\frac{k_3}{d}\right\} & \lambda & = 1 - c \\
\nu_\text{GV} & = 1 - \left\{\frac{k_2}{d}\right\} - \left\{\frac{k_3}{d}\right\} & \mu & = c - a - b \\
\lambda_\text{GV} & = 1 - \left\{\frac{k_1}{d}\right\} - \left\{\frac{k_2}{d}\right\} & \nu & = b - a
\end{align*}
The hyperelliptic curve in Section~4 is
\[ y^d = (x - \alpha_1)^{k_1} (x - \alpha_2)^{k_2} (x - \alpha_3)^{k_3}. \]

Dihedral case (Theorem~2):
\begin{align*}
\frac{k_1}{d} & = \frac{p}{2m} \\
\frac{k_2}{d} & = \frac{p}{2m} \\
\frac{k_3}{d} & = \frac{m - p}{2m}
\end{align*}
Note that $\lambda = p'/m$ with $p + p' = m$. The hyperelliptic curve is
\[ y^d = (x - \alpha_1)^{k_1} (x - \alpha_2)^{k_2} (x - \alpha_3)^{k_3}. \]
Cosines appear in Section~2.3: $x_j = \exp(2\pi i\,\tfrac{k_j}{d})$, and we work in the totally real field $\mathbb{Q}(\cos(\frac{2\pi}{m}))$.

Airy case:
\begin{align*}
\frac{k_1}{d} & = \frac{1}{3} \\
\frac{k_2}{d} & = \frac{1}{3} \\
\frac{k_3}{d} & = \frac{1}{6},
\end{align*}
so $(k_1, k_2, k_3, d) = (2, 2, 1, 6)$, and the hyperelliptic curve is
\[ y^6 = (x - \alpha_1)^2 (x - \alpha_2)^2 (x - \alpha_3). \]

@@

\textcolor{magenta}{[For this, we lift to a countable cover; see {\tt airy-resurgence.tex}, currently \S 6.4]}

@@

\subsection{Building a distinguished frame of analytic solution}
\subsubsection{Going to the spatial domain}\label{spatial}
%\subsubsection{The big idea}\label{big-idea}
We are going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel}. We will succeed when $\alpha^2 - 1 = 0$, and we will see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.

>>>>

\subsubsection{Asymptotic analysis}

@@

The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
\begin{align*}
& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
\end{align*}
as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}. Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
\color{DarkCyan}
Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
where $\zeta = -1 + \zeta_{-1}$.
\color{black}

@@

\subsubsection{Lifting to a countable cover}
Formula~\ref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$. Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.

Setting $u = \cosh(t/n)$ and recalling that
\begin{align*}
\cosh(n\tau) & := T_n(\cosh(\tau)) \\
\sinh(m\tau) & := U_{m-1}(\cosh(\tau)) \sinh(\tau),
\end{align*}
we can rewrite formula~\ref{integral:mod-bessel-rational} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
\begin{align}
\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
\end{align}
For any $\nu \in \C \smallsetminus \Z$, formulas~10.27.4 and 10.32.12 from \cite{dlmf} tell us that
\begin{align}
\notag K_\nu(z) & = \frac{\pi}{\sin(\nu \pi)} \cdot \frac{1}{2}\big[ I_{-\nu}(z) - I_\nu(z) \big] \\
\notag & = \frac{1}{2i \sin(\nu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\nu t} - e^{-\nu t}\right]\,dt \\
\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\nu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\nu t)\,dt,
\end{align}
where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$. The integral converges when $z$ is in the right half-plane. We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\nu = m/n$.

When $\nu$ goes to $0$, formula~\eqref{integral:mod-bessel-lifted} becomes
\[ K_0(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
\begin{align*}
K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
\end{align*}
with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.

@@

\subsection{Building a distinguished frame of analytic solutions}
\subsubsection{Going to the spatial domain}\label{spatial}
%\subsubsection{The big idea}\label{big-idea}
We are going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel}. We will succeed when $\alpha^2 - 1 = 0$, and we will see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
